Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-22 Papers/ms.tex
Paragraphs

\section{The Cosmic Horseshoe}
As a further demonstration the method, we apply it to the X-band INT
image of the Cosmic Horseshoe \citep{}, which is shown in
Figure~\ref{fig:horseshoe_image}.

@@

\bibitem[\protect\citeauthoryear{Huppenkothen et 
al.}{2015}]{magnetron} Huppenkothen D., et al., 2015, arXiv, 
arXiv:1501.05251

>>>>

\section{The Cosmic Horseshoe}
As a further demonstration the method, we apply it to the X-band data
from the Isaac Newton Telescope (INT). This image of the Cosmic Horseshoe
\citep{}, which is shown in Figure~\ref{fig:horseshoe_image}. For this system,
more data is available (Y and Z band data, as well as more recent
Hubble Space Telescope (HST) imaging). Unfortunately our current implementation
doesn't allow for multi-band data (unlike \citet{2011MNRAS.412.2521B}), and
is quite slow when running on the larger HST image. Therefore this section
should be considered a further demonstration of the technique, and not a
thorough study of this system.

@@

\bibitem[\protect\citeauthoryear{Huppenkothen et 
al.}{2015}]{magnetron} Huppenkothen D., et al., 2015,
accepted for publication in ApJ. arXiv:1501.05251
